---
title: "Individual Assignment 8"
output: html_document
date: '2022-11-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem8
```{r}
library(ISLR)
attach(Carseats)
set.seed(1)
train=sample(1:nrow(Carseats),nrow(Carseats)/2)
test=(-train)
summary(Carseats)
Sales.test=Sales[-train]
```
# (d)
```{r}
library(randomForest)
set.seed(2)
bag.car=randomForest(Sales~.,data=Carseats,subset=train,mtry=10,importance=TRUE)
bag.car
```
```{r}
yhat.bag=predict(bag.car,newdata=Carseats[test,])
plot(yhat.bag,Sales.test)
```


```{r}
mean((yhat.bag-Sales.test)^2)
```
### The test MSE is 2.586535

```{r}
importance(bag.car)
varImpPlot(bag.car)
```
### Price and ShelveLoc are the most important variables.
# (e)
```{r}
for (i in 1:10){
  set.seed(2)
  rf.car=randomForest(Sales~.,data=Carseats,subset=train,mtry
                       =i,importance=TRUE)
  yhat.rf=predict(rf.car,newdata=Carseats[test,])
  print(mean((yhat.rf-Sales.test)^2))
}
```
### When m gets bigger, test MSE drops drastically at first but slows down when it gets even bigger. For this reason, it might be the most efficient to choose m=6
```{r}
set.seed(2)
bag.car6=randomForest(Sales~.,data=Carseats,subset=train,mtry=6,importance=TRUE)
yhat.bag6=predict(bag.car6,newdata=Carseats[test,])
importance(bag.car6)
varImpPlot(bag.car6)
```
### Price and ShelveLoc are the most important variables when m=6.

# Problem10
# (a)
```{r}
library(ISLR)
sum(is.na(Hitters$Salary))
hitters=na.omit(Hitters)
sum(is.na(hitters$Salary))
hitters$Salary=log(hitters$Salary)
```
# (b)
```{r}
train=1:200
test=201:nrow(hitters)
hitters.test=hitters$Salary[test]
```
(c) Perform boosting on the training set with 1,000 trees for a range of values of the shrinkage parameter λ. Produce a plot with different shrinkage values on the x-axis and the corresponding training set MSE on the y-axis.
# (c)
```{r}
library(gbm)
set.seed(3)
mse=vector(mode = "numeric")
grid=10^seq(-10,0,by=0.05)
for (i in 1:length(grid)){
  boost.hittersi = gbm(Salary~.,hitters[train,],distribution = "gaussian", n.trees=1000,shrinkage = grid[i])
  pred.boost=predict(boost.hittersi,newdata=hitters[train,], n.trees = 1000)
  mse[i] = mean((pred.boost - hitters$Salary[train])^2)
}
plot(grid,mse)
```
# (d)
```{r}
for (i in 1:length(grid)){
  boost.hitters = gbm(Salary~.,hitters[train,],distribution = "gaussian", n.trees=1000,shrinkage = grid[i])
  pred.boost=predict(boost.hitters,newdata=hitters[test,], n.trees = 1000)
  mse[i] = mean((pred.boost - hitters$Salary[test])^2)
}
plot(grid,mse)
```
#(e)
```{r}
#linear model
lm.mod=lm(Salary~.,data=hitters[train,])
lm.pred=predict(lm.mod,hitters[test,])
mean((lm.pred-hitters.test)^2)
```

```{r}
#Ridge regression
library(glmnet)
x = model.matrix(Salary~.,data=hitters[train,])
x.test=model.matrix(Salary~.,data=hitters[test,])
y = hitters$Salary[train]
ridge.mod=glmnet(x,y,alpha=0)
ridge.pred=predict(ridge.mod,s=0.01,newx=x.test)
mean((ridge.pred-hitters.test)^2)
```

```{r}
#boosted trees
set.seed(5)
boost.hitters = gbm(Salary~.,hitters[train,],distribution = "gaussian", n.trees=1000)
pred.boost=predict(boost.hitters,newdata=hitters[test,], n.trees = 1000)
mean((pred.boost-hitters.test)^2)
```
### Among three different approaches, boosted trees model has the lowest test MSE
# (f)
```{r}
summary(boost.hitters)
```
### CAtBat is the most important predictor.
# (g)
```{r}
set.seed(5)
bag.hit=randomForest(Salary~.,data=hitters,subset=train,mtry=19,importance=TRUE)
yhat.hit=predict(bag.hit,newdata=hitters[test,])
mean((yhat.hit-hitters.test)^2)
```
