---
title: "Individual assignment4"
output: html_document
date: '2022-09-29'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ISLR)
attach(Weekly)
summary(Weekly)
```
# 10.(d)
```{r}
train=(Year<2009)
testing=Weekly[!train,]
Direction.2010=Direction[!train]
glm.fit=glm(Direction ~ Lag2, data = Weekly, subset = train,family = binomial)
glm.probs=predict(glm.fit,testing,type="response")
glm.pred=rep("Down",dim(testing)[1])
glm.pred[glm.probs>0.5]="Up"
table(glm.pred,Direction.2010)
mean(glm.pred==Direction.2010)
```
### The overall fraction of correct predictions is 62.5%.

# (f)
```{r}
library(MASS)
qda.fit=qda(Direction ~ Lag2, data = Weekly, subset = train)
qda.class=predict(qda.fit,testing)$class
qda.class
table(qda.class,Direction.2010)
mean(qda.class==Direction.2010)
```
### The overall fraction of correct predictions is about 58.7%.

# 8. (a)
```{r}
set.seed(1)
x=rnorm(100)
y=x-2*x^2+rnorm(100)
```
### n=100 and p=2, the model used is Y = X - 2X^2 + ε.

# (b)
```{r}
plot(x,y)
```

### As the plot shown, there is a curved relationship between x and y.

# (c)
## i.
```{r}
set.seed(1)
data.cv=data.frame(x,y)
library(boot)
glm.fiti=glm(y ~ x)
cv.err=cv.glm(data.cv,glm.fiti)
cv.err$delta[1]
```
## ii.
```{r}
glm.fitii=glm(y ~ poly(x,2))
cv.err2=cv.glm(data.cv,glm.fitii)
cv.err2$delta[1]
```
## iii.
```{r}
glm.fitiii=glm(y ~ poly(x,3))
cv.err3=cv.glm(data.cv,glm.fitiii)
cv.err3$delta[1]
```
## iv.
```{r}
glm.fitiv=glm(y ~ poly(x,4))
cv.err4=cv.glm(data.cv,glm.fitiv)
cv.err4$delta[1]
```

# (d)
## i.~iv.
```{r}
set.seed(2)
data.cvd=data.frame(x,y)
library(boot)
cv.error=rep(0,4)
for(i in 1:4){
  glm.fitd=glm(y ~ poly(x,i),data = data.cvd)
  cv.error[i]=cv.glm(data.cvd,glm.fitd)$delta[1]
}
cv.error
```
### The results are the same as I got in (c) beacuse the validation set sizes only 1 and the validation repeats the process for n times, leading to the same average MSE.

# (e)
### Model ii has the smallest LOOCV error, it is expected because the relation between x and y is quadratic.

# (f)
```{r}
summary(glm.fiti)
```
```{r}
summary(glm.fitii)
```
```{r}
summary(glm.fitiii)
```
```{r}
summary(glm.fitiv)
```
### According to the summary of the models, the coefficient of x^3 and x^4 do not have p-value<0.05 to reject the hypothesis, and the coefficient of x and x^2 have statistical significance. And the results are correspondent with the fact that Model ii has the smallest LOOCV error.